\bf Turkish Elections and Catastrophic Events

### 2021-12-07 paper/main.tex
paperr

A year ago, Turkey celebrated it's first century of being a democracy and only in 2 years, celebrations for being a republic is on the line. Yet, the country, which resides possibly one of the lesser stable regions in the world; suffered a lot during this period, while trying to establish their democratic traditions. Having survived 3 coups,

\section{Literature Review}

>>>>

A year ago, Turkey celebrated a century of being a democracy. Now, only 2 years away from the same milestone for being a republic, it is inevitable to think and analyse the trends of Turkish democracy. 
It is reasonable to say, Turkey, which resides possibly one of the lesser stable regions in the world; suffered a lot during this period, while trying to establish their democratic traditions. Having survived 3 coups, 3 "soft" coups and numerous economic, political and civil crises, Turkey still maintained regular and somewhat fair elections without interruption, unlike many other countries in a similar political landscape. The goal of this paper is to materialise this continuity and uncover the impact of catastrophic events in Turkey to voting behavior and results.

\section{Background}

\section{Data and Limitations}

The data is retrieved retrieved from Turkish Statistical Institute, which is the main source for census and election data in Turkey. It consists municipal and parliamentary election results. Having decided to have a public vote for the president in 2010, Turkey had it's first presidential elections in 2014. Since there only has been one more presidential election after, this type of elections are not included in the analysis.
